---
title: "Slide Rmd"
subtitle: "test and template"
author: "Lanera Corrado\\thanks{Unit of Biostatistic, Epidemiology and Public Healt\\newline Department of Cardiac, Thoracic and Vascular Sciences (University of Padua)}"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  beamer_presentation: 
    fig_caption: yes
    keep_tex: yes
    theme: Padova
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## References
