---
title: "Slide Rmd"
subtitle: "test and template"
author: "Lanera Corrado\\thanks{Unit of Biostatistic, Epidemiology and Public Healt\\newline Department of Cardiac, Thoracic and Vascular Sciences (University of Padua)}"
date: "`r format(Sys.time(), '%d %B, %Y')`"
header-includes:
   - \usepackage{booktabs}
   - \usepackage{subfig}
   - \usepackage{multicol}
output: 
  beamer_presentation: 
    fig_caption: yes
    keep_tex: yes
    theme: Padova
classoption: [a4paper]
bibliography:
   - bibliography.bib
   - pkg_bib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# From standard RStudio template

## R Markdown
<!-- This way you can comment the source code -->

This is an R Markdown presentation. Markdown is a simple formatting syntax 
for authoring HTML, PDF, and MS Word documents. For more details on using 
R Markdown see <http://rmarkdown.rstudio.com>.
<!-- note: a texted link is made by [text](link) -->

When you click the **Knit** button a document will be generated that
includes both content as well as the output of any embedded R code chunks
within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

# Something more

## LaTeX

Out of headers, you can use as \LaTeX{} as you need.

> __But you do not have to mix markdown with \LaTeX!!.__

You can create a footnote using markdown syntax `\^[footnote]` or \LaTeX{}
syntax `\footnote{footnote}`,
but remember to be syntax-consistent while nesting markup, i.e

both the following are 0K

    ^[A __bold__ text in a footnote.]
    \footnote{A \textbf{bold} text in a footnote.}

but both of the following return an error

    ^[A \textbf{bold} text in a footnote]
    \footnote{A *bold* text in a footnote}


## Table, caption and cross references

The using of standard \LaTeX{} can run in help to create (referenced) tables


\begin{table}
\centering
\caption{my first table.}
\label{tab:first}
\begin{tabular}{lc}
\toprule
topic  & value\\
\midrule
first  & 1    \\
second & 2    \\
\bottomrule
\end{tabular}
\end{table}

In a slide you can always provide references, e.g. to the Table&nbsp;\ref{tab:first}.

<!-- &nbsp; is the "No Breaking SPace" HTML tag -->

> __avoid references across different slides...__


## Multicolumns and Tabular figures


<!-- subfloat needs *subfig*a package-->

\begin{multicols}{2}

\begin{figure}
\centering
\subfloat[][\emph{figure 1.1 JPG}]
    {\includegraphics[width = .45\linewidth]{Figure/padoval.jpg}} \quad
\subfloat[][\emph{figure 1.2 EPS}]
    {\includegraphics[width = .45\linewidth]{Figure/l1lasso.eps}} \\
%
\subfloat[][\emph{figure 2.1 PNG}]
    {\includegraphics[width = .8\linewidth]{Figure/feed2_plot.png}}
\caption{Three tabularized figures.}
\label{fig:first}
\end{figure}

\vfill
\columnbreak


\vspace*{\fill} % this needs only for vertical centering
\begin{figure}
\centering
\includegraphics[width = .95\linewidth]{Figure/boom.png}
\caption{A simple, single, figure --- \url{http://xkcd.com/795/}}
\label{fig: simple}
\end{figure}
\vspace*{\fill} % this needs only for vertical centering

\end{multicols}

## Reference an article or an R-package

You can refer to an article using the markdown \@\<label\> (see @art1).

Moreover you can ask to R (inside a chunk in this own markdown) to create a
`.bib` file with the citations for the packages you need to cite, and citing
them by the name of the package adding the prefix __R-__

E.g. to cite the documentation of dplyr (see @R-dplyr) use \@R-dplyr, and
add dplyr to the list of your *citable* package in a chunk including code
like the following one


    knitr::write_bib(
        c('dplyr', 'stringr'),
        file = 'pkg_bib.bib'
    )


## Thank you

\begin{center}
\Huge{Thank you}
\end{center}

## References
```{r pkg_bib, include = FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(
    x    = c(
        'dplyr', 'stringr'
    ),
    file = 'pkg_bib.bib'
)
```

<!--
The references are auto included at the very end of the document.
So, on one hand you can write command that influence them (e.g. changing
the font size), on the other hend you cannot insert supplementary matherials
after the references.
-->

\scriptsize



